\Huge{Versioned Datasets and Queries in RDF/SPARQL}

### 2019-03-12 paper.tex
added bibliography file and made some progress on the related work section

\section{Related Work}

\section{Preliminaries} % Maybe not
\section{(Method)} % Name of our method goes here
\section{Evaluation} % This two sections can
\section{Results}    % be merged for better flow
\section{Conclusion}
\newpage
\bibliographystyle{unsrt}
\bibliography{propuesta}
\end{document}

>>>>

\section{Related Work}
Gutierrez et al.~\cite{GutierrezHV07} describe a framework that allows time representation in RDF using annotations. An important distinction to make is that their work is focused on \textbf{labeling} over \textbf{versioning}; \textbf{labeling} means adding meta-data to query result validity, meanwhile \textbf{versioning} implies simultaneously keeping several versions of the same dataset. This work also formally defines labels and time intervals, but does not cover an implementation for either.

Zimmerman et. al~\cite{DBLP:journals/ws/ZimmermannLPS12} extend RDF to allow generalized annotations which can, in particular, be used to add validity time intervals to each triple.
\section{Preliminaries} % Maybe not
\section{(Method)} % Name of our method goes here
\section{Evaluation} % This two sections can
\section{Results}    % be merged for better flow
\section{Conclusion}
\newpage
\bibliographystyle{unsrt}
\bibliography{paper}
\end{document}
